---
title: "osmdata_starter"
author: "Martin Monkman"
date: "23/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# package load
library(osmdata)
library(sf)

library(ggplot2)
```


## 1. bounding box

{osmdata} function `opq()` to define the bounding box.

```{r}
# Victoria point
vic_long = -123.3576
vic_lat = 48.4262


# Victoria CMA bounding box dimensions
vic_long_e <- -123.25
vic_long_w <- -123.5
vic_lat_n <- 48.75
vic_lat_s <- 48.2

```


Define the bounding box (note `c(xmin, ymin, xmax, ymax)` which equates to west-south-east-north sequence)

Add map features using `add_osm_feature`

* see https://docs.ropensci.org/osmdata/reference/available_features.html

```{r}
yvr_bb <- opq(bbox = c(vic_long_w, vic_lat_s, vic_long_e, vic_lat_n)) %>% 
  add_osm_feature(key = "natural", 
                  value = "coastline") %>% 
  osmdata_sf()

yvr_bb
```


```{r}
ggplot() + 
  geom_sf(data = yvr_bb$osm_lines,
          inherit.aes = FALSE,
          colour = "blue")
```



Alternatively, we can use the predefined name of Victoria. As we shall see, this covers the City of Victoria, and not the entire region.

```{r}
# use the name
getbb("Victoria BC")

# coastline
yvr_bb_n <- getbb("Victoria BC") %>% 
  opq() %>% 
  add_osm_feature(key = "natural", 
                  value = "coastline") %>% 
  osmdata_sf()

# roads
yvr_bb_r <- getbb("Victoria BC") %>% 
  opq() %>% 
  add_osm_feature(key = "highway") %>% 
  osmdata_sf()
```

plot

```{r}
  
ggplot() + 
  geom_sf(data = yvr_bb_n$osm_lines,
          inherit.aes = FALSE,
          colour = "blue") +
  geom_sf(data = yvr_bb_r$osm_lines,
          inherit.aes = FALSE,
          colour = "black")

```





#vic_basemap <- get_map(location=c(lon = vic_long, lat = #vic_lat), zoom=11, maptype = 'terrain-background', source = #'stamen')

#ggmap(vic_basemap)



vic_basemap <- get_map(location=c(lon = vic_long, lat = vic_lat), 
                       zoom=13, 
                       maptype = 'roadmap', 
                       source = 'osm')

ggmap(vic_basemap)



# Define a function to fix the bbox to be in EPSG:3857
ggmap_bbox <- function(map) {
  if (!inherits(map, "ggmap")) stop("map must be a ggmap object")
  # Extract the bounding box (in lat/lon) from the ggmap to a numeric vector, 
  # and set the names to what sf::st_bbox expects:
  map_bbox <- setNames(unlist(attr(map, "bb")), 
                       c("ymin", "xmin", "ymax", "xmax"))
  
  # Coonvert the bbox to an sf polygon, transform it to 3857, 
  # and convert back to a bbox (convoluted, but it works)
  bbox_3005 <- st_bbox(st_transform(st_as_sfc(st_bbox(map_bbox, crs = 4326)), 3005))
  
  # Overwrite the bbox of the ggmap object with the transformed coordinates 
  attr(map, "bb")$ll.lat <- bbox_3005["ymin"]
  attr(map, "bb")$ll.lon <- bbox_3005["xmin"]
  attr(map, "bb")$ur.lat <- bbox_3005["ymax"]
  attr(map, "bb")$ur.lon <- bbox_3005["xmax"]
  map
}



```

